LAGOS lake depth

### 2020-01-15 figures/00_maps.Rmd
rm duplicate measures based on program reliability

dt_plot <- dplyr::select(lg$locus$locus_information, 
                         -contains("decdeg"), 
                         -contains("states"), 
                         -contains("gnis")) %>%
  distinct(lagoslakeid, .keep_all = TRUE) %>%
  left_join(dt, by = "lagoslakeid") %>%
  dplyr::filter(lake_waterarea_ha >= 4) %>%
  group_by(lake_centroidstate) %>%
  summarize(prop_maxdepth = mean(!is.na(lake_maxdepth_m))) %>%
  arrange(desc(prop_maxdepth)) %>%
  left_join(dplyr::filter(
    dplyr::select(states_all, postal, iso_a2), iso_a2 == "US"), 
            by = c("lake_centroidstate" = "postal")) %>%
  dplyr::filter(!is.na(prop_maxdepth))
st_geometry(dt_plot) <- dt_plot$geom

>>>>

dt_plot <- dt %>%
  distinct(lagoslakeid, .keep_all = TRUE) %>%
  dplyr::filter(lake_waterarea_ha >= 4) %>%
  group_by(lake_state) %>%
  summarize(prop_maxdepth = mean(!is.na(lake_maxdepth_m))) %>%
  arrange(desc(prop_maxdepth)) %>%
  left_join(dplyr::filter(
    dplyr::select(states_all, postal, iso_a2), iso_a2 == "US"), 
            by = c("lake_state" = "postal")) %>%
  dplyr::filter(!is.na(prop_maxdepth))
st_geometry(dt_plot) <- dt_plot$geom
